Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth,scale=5]{resources/ch3/alur_v2.png}
	\caption{PRA system flow}
	\label{flow-pra}
\end{figure}

@@

\subsection{Implementation}

>>>>

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth,scale=5]{resources/ch3/alur_v2.png}
	\caption{PRA system workflow}
	\label{flow-pra}
\end{figure}

@@

\subsection{Implementation}
Implementation of the performance regression analysis (PRA) system will be made based on the architectural design as shown in Fig. \ref{arch-pra}. Component
like the instrumentation library instead will use the available
Open Source distributed tracing solution from Zipkin. Components to be made from scratch
is entirely the PRA User Interface (UI) and PRA Engine components of the system
PRA will perform the main computation of the detection system and regression analysis.
The PRA Engine component will also serve as an API that will be accessed by
PRA UI component.

\subsubsection{PRA Engine Implementation}

\subsubsection{PRA UI Implementation}
